Self-test prime dimensional EPR pairs with constant alphabet

### 2019-02-03 Draft/draft.tex
Made comments (in blue) on the first 6 pages.

@@

In order to accomplish our goal, we introduce new techniques for self-testing.
First of all, we use a different variant of the weighted CHSH inequality to enforce the eigenvalue of
some unknown operator which is the product of two binary observables used in the weighted CHSH test.
The variant of the CHSH inequality that we use is not used in the self-testing literature before.
Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintains
certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
Intuitively, such decomposition can be seen as the inverse of the Jordan's lemma decomposition.
The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
which is the core idea in all the previous self-testing results. 
Instead, we find a new pair of operators that can generate the ring of matrices over complex numbers.

@@

We use some basic number theory in our work. A primitive root of a prime number
$d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
$r$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$ where
$\Z_d^\times = \{1,2\dots d-1\}$. When we say $d$ has primitive root $r$, we always mean
that $r$ is the smallest primitive root.

@@

We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
\begin{align}
	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
\end{align}
where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
and $r$ is the primitive root of $d$.
Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
unless otherwise specified, for example, the $k/r$ above.

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 1,2$ 
on Hilbert space $\calH_A$ and $\calH_B$ respectively.
A binary observable is a Hermitian matrix whose only eigenvalues are either $+1$ or $-1$.
The weighted CHSH inequality is given by 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
\end{align}
where $\ip{A_xB_y}$ is the expectation value of of the observables.
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \I_\alpha \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
measurements up to isometry, 
which is a phenomenon referred as a self-test. We give formal statement of this self-testing result in \cref{sec:chsh}.

\textbf{Nonlocal games}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. Such games are nonlocal
because Alice and Bob cannot communicate after getting their questions but they may share some strategy before 
the start of the game. Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
pair to $\{0.1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
to our new result.

A quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side, 
$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where a projective measurement $P$ satisfies
the condition that $P^2 = P = P\ct$.
Then Alice and Bob's quantum strategy produces the correlation
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
%Note that we may use the term behaviour and correlation interchangeably.
%The value of a strategy is given by
%\begin{align}
%	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
%\end{align}

The main contribution of our work is the construction of a correlation, which is the combination of 
the optimal correlation of a linear system game with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
and the optimal correlation to violate the weighted CHSH inequality.
The special property of the correlation is that it can self-test $\ket{\EPR{d-1}}$ for arbitrary $d$ with certain 
primitive root. 
In the next part, we introduce the definition of self-testing, the definition of linear system game, 
and its operator solution, 
following definitions given in Ref.~\cite{coladan2017, slofstra2017}.
\begin{definition}[Self-testing]
	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
	such that 	
	\begin{align*}
		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
	\end{align*}
\end{definition}
\begin{definition}[Linear system game]
 Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
 that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
 Formally, the winning condition is 
 \begin{align*}
 	a(j) &= b && \text{(Consistency)} \\
	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
 \end{align*}
 for all $(i,j) \in \calX \times \calY$.
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.
We focus on quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy for the linear system game $(Hx = c)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement, and
vice versa.

It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
operator solution in the following sense.
\begin{definition}[Operator solution of a linear system]
\label{def:op_sol}
	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of bounded Hermitian 
	operators $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that 
	\begin{enumerate}
		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
		\item for all $1 \leq i \leq m$,
		\begin{align*}
			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
		\end{align*}
	\end{enumerate}
	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
	solution in which the Hilbert space is finite-dimensional.
\end{definition}
Perfect quantum strategies can be extracted from operator solutions and vice versa.
Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
over $\Z_2$, which is called the solution group.
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,c) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
For concepts about group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 
a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.

@@

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
The goal of this section and the following two sections is to 
present a correlation that can self-test $\ket{\EPR{d-1}}$, 
where $d$ is prime and has primitive root $r \in \{2, 3, 5\}$,
and this correlation is denoted by $C(\dr{r})$.
The correlation we constructed is the optimal correlation for a game $\G(\dr{r})$, which is the combination of two tests.
In this section, we introduce the linear system game which tests a relation that should be satisfied by 
Alice and Bob's observables.

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.
The main component of $\G(\dr{r})$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg_r= \langle u, x : uxu^{-1} = x^r \rangle, \text{ for } r \in \{2, 3,5\}.
\end{align}
In other words, relations in the presentation of the solution group of $\LS_r$ can be combined to derive the
relation $uxu^{-1} = x^r$.
\begin{proposition}
	\label{prop:embed}
	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
	with constant numbers of variables and equations, where each equation involves $3$ variables.
\end{proposition}
The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Ref.~\cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
and \cref{sec:power5} for $r = 5$.

In the later parts of the paper, we use $n_r$ and $m_r$ to refer to the size of $\LS_r$.
The key feature of this embedding is that $\LS_r$ has constant-sized input-output alphabet
even if the generators $u$ and $x$ have arbitrary order. 
The product of the generators $x_1$ and $x_2$ from the solution group of $\LS_r$ plays the role 
of the generator $x$ in $\Pg_r$ and the product of the generators $x_3$ and $x_4$ plays the role
of the generator $u$ in $\Pg_r$. As shown in \cref{sec:power2}, \cref{sec:power3} and \cref{sec:power5}, 
$x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
\begin{align}
	(x_3x_4)(x_1x_2)(x_4x_3) = (x_1x_2)^r.
\end{align}
Hence the perfect quantum strategy $(\ket{\psi}, \{A_i, B_i\}_{i=1}^n)$ should satisfy 
the key relation that 
\begin{align}
	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^r\ket{\psi}, 
\end{align}
and similarly on Bob's side.
If we denote the unitary corresponding to the generator $u$ of $\Pg_r$ by $U$ and the unitary
corresponding to $x$ by $X$, then $U = A_3A_4$, $X= A_1A_2$, and 
$UXU\ct \ket{\psi} = X^r \ket{\psi}$.
The special property of $U$ and $X$ is summarized in the following lemma.

\begin{lemma}
	\label{lm:ux_independ}
	Suppose there exist unitaries $U$ and $X$ which have the following forms
	\begin{align}
		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/r}{i},
	\end{align}
	where $d$ is an odd prime number with primitive root $r$,
	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
\end{lemma}
Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^r$.
In the self-test proof, this lemma will be a critical step.
\begin{proof}
We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
such that 
\begin{align}
	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
\end{align}
We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $r^{k_i} \equiv i \pmod{d}$.
The fact that $r$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.

>>>>

\def\carl#1{{\color{blue} #1 -Carl}}

@@

In order to accomplish our goal, we introduce new techniques for self-testing.
First of all, we use a different variant of the weighted CHSH inequality to enforce the eigenvalue of
some unknown operator which is the product of two binary observables used in the weighted CHSH test.
\carl{I think this game might have been defined in APM12, and if so we need to cite it.}
The variant of the CHSH inequality that we use is not used in the self-testing literature before.
Secondly, we give a new way to decompose unitaries of arbitrary order into binary observables which maintains
certain commutation relations. Such decomposition is different from what Slofstra used in his work \cite{slofstra2017}.
\carl{Our work is heavily based on \cite{slofstra2017}, and we need to make that clearer.}
Intuitively, such decomposition can be seen as the inverse of the Jordan's lemma decomposition.
The third contribution is that we prove self-testing without using anti-commutation relations between Pauli operators, 
which is the core idea in all the previous self-testing results.
\carl{Are we sure about that ("all")?}
Instead, we find a new pair of operators that can generate the ring of matrices over complex numbers.

@@

We use some basic number theory in our work. A primitive root of a prime number
$d$ is an integer $r$ such that $r \pmod{d}$ has multiplicative order $d-1$. Equivalently,
$r$ is the generator of the multiplicative group of integers modulo $d$, $\Z_d^\times$ where
$\Z_d^\times = \{1,2\dots d-1\}$. When we say $d$ has primitive root $r$, we always mean
that $r$ is the smallest primitive root.  \carl{I'm not clear on what that last sentence means.  You just defined what a primitive root
is --- are you changing the definition now?}

@@

We self-test $\ket{\EPR{d-1}}$ by verify that Alice and Bob has operators
\begin{align}
	X = \sum_{k=1}^{d-1} \omega_d^k\ketbra{k}{k} && U = \sum_{k=1}^{d-1} \ketbra{k/r}{k},
\end{align}
where $\omega_d = e^{i2\pi/d}$ is the primitive $d$-th root of unity,
and $r$ is the primitive root of $d$.  \carl{That sentence is jumping ahead --- you should just stick to
definitions and notation for now.}
Through out this paper, any operation on the label of the eigenvector $\ket{k}$ is taken modulo $d$,
unless otherwise specified, for example, the $k/r$ above.

\textbf{The weighted CHSH inequality \cite{acin2012}.}
The first building-block of our result is a robust self-testing result based on the weighted CHSH inequality.
In the CHSH scenario, Alice and Bob has binary observables $A_x,B_y$ for $x,y = 1,2$ 
on Hilbert space $\calH_A$ and $\calH_B$ respectively.  \carl{It needs to be clearer who Alice and Bob
are --- perhaps you should put this subsection after the ``Nonlocal games'' subsection.}
A binary observable is a Hermitian matrix whose only eigenvalues are either $+1$ or $-1$.
The weighted CHSH inequality is given by 
\begin{align}
	\label{eq:chsh_op}
	\I_\alpha = \alpha\ip{A_1B_1}+\alpha\ip{A_1B_2} + \ip{A_2B_1} - \ip{A_2B_2}\leq 2\alpha,
\end{align}
where $\ip{A_xB_y}$ is the expectation value of of the observables.  \carl{Same here -- it's not clear enough
what this means until the reader has seen the ``Nonlocal games'' subsection.}
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$, they cannot violate
the weighted CHSH inequality.
However, If they share entangled state $\ket{\psi}$, the maximal violation is 
\begin{align}
\label{eq:chsh_max}
 \I_\alpha \leq 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy for $\I_\alpha$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$ (i.e. achieving maximal violation in \cref{eq:chsh_max})
	consists of the joint state $\ket{\EPR{2}}$ and observables $A_1 = \pauliz$, $A_2 = \paulix$,
	$B_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $B_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
\carl{Just to be complete, you should say what $\pauliz$ and $\paulix$ denote.}
An interesting observation of the weighted CHSH inequality is that its maximal violation can certify the shared states and the 
measurements up to isometry, 
which is a phenomenon referred as a self-test. We give formal statement of this self-testing result in \cref{sec:chsh}.

\textbf{Nonlocal games}. The two players of a nonlocal game are Alice and Bob. Each of them is requested
to give an answer for a randomly chosen question. We denote Alice's question set by $\calX$ and answer set by $\calA$. Similarly,
Bob's question set is denoted by $\calY$ and his answer set is denoted by $\calB$. The nonlocal game also
comes with two functions: $\pi: \calX \times \calY \rightarrow [0,1]$, which is the probability distribution over the questions,
and $V: \calA \times \calB \times \calX \times \calY \rightarrow \R$, which is the scoring function. Such games are nonlocal
because Alice and Bob cannot communicate after getting their questions but they may share some strategy before 
the start of the game. Note that in the literature, the typical scoring function of a nonlocal game maps the input-output
pair to $\{0,1\}$ which corresponds to losing and winning. Allowing the score to be any real number is the key ingredient 
to our new result.

A quantum strategy of a game $G$ consists of projective measurements $\{\{A_x^a\}_a\}$ on Alice's side, 
$\{\{B_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where a projective measurement $P$ satisfies
the condition that $P^2 = P = P\ct$.  \carl{You need to put explicit labels on the quantum systems used by
Alice and Bob.  (Later on you seem to use ``$A$'' and ``$B$'' to refer to those systems, but those are also
the same letters you use for Alice's and Bob's measurements.  That's confusing.)}
Then Alice and Bob's quantum strategy produces the correlation
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
where $(A_x^a)^2 = A_x^a = (A_x^a)^\dagger$ and $(B_y^b)^2 = B_y^b = (B_y^b)^\dagger$.
%Note that we may use the term behaviour and correlation interchangeably.
%The value of a strategy is given by
%\begin{align}
%	\omega(G,p)  = \sum_{a,b,x,y} \pi(x,y) \pr{ab}{xy} V(a,b,x,y).
%\end{align}

The main contribution of our work is the construction of a correlation, which is the combination of 
the optimal correlation of a linear system game with constant-sized $\calX$,$\calY$,$\calA$ and $\calB$
and the optimal correlation to violate the weighted CHSH inequality.  \carl{The reader does not 
know yet what a linear system game is, so this comment is more confusing than helpful.}
The special property of the correlation is that it can self-test $\ket{\EPR{d-1}}$ for arbitrary $d$ with certain 
primitive root. 
In the next part, we introduce the definition of self-testing, the definition of linear system game, 
and its operator solution, 
following definitions given in Ref.~\cite{coladan2017, slofstra2017}.

\carl{Before the next definition, you should define what a ``correlation'' is.}
\begin{definition}[Self-testing]
	We say that a correlation self-tests a quantum state $\ket{\psi}$, if 
	the correlation is produced by a strategy with shared state $\ket{\psi}$, and 
	for any quantum strategy $S = ( \{\tA_x\}, \{\tB_y\}, \ket{\tpsi})$ that produces the same correlation,
	there exists local isometries $\Phi_A$ and $\Phi_B$ on Alice and Bob's side and a state $\ket{junk}$ 
	such that 	
	\begin{align*}
		\Phi_A \x \Phi_B \ket{\tpsi} =  \ket{\psi} \x \ket{junk}.
	\end{align*}
\end{definition}
\begin{definition}[Linear system game]
 Let $Hx = c$ be an $m \times n$ system of linear equations over $\Z_2$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2 = \{0,1\}$ and 
 $c$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = [m]+1$ and replies with $a \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = [n]+1$ and replies with an assignment $b \in \calB = \Z_2$. The winning condition is 
 that Alice's assignment to the variables should satisfy equation $i$ and Alice's $j$-th assignment $a(j)$ should match $b$.
 Formally, the winning condition is 
 \begin{align*}
 	a(j) &= b && \text{(Consistency)} \\
	\sum_{k= 1}^n H(i,k) a(k) &\equiv c(i) \pmod 2. &&\text{(Constraint satisfaction)},
 \end{align*}
 for all $(i,j) \in \calX \times \calY$. 
\end{definition}
The scoring function of linear system games always maps an input-output pair to $\{0,1\}$, 
so later when we say a quantum strategy wins a linear system game perfectly, we mean that 
$V(a,b,x,y) =0$ implies that $\pr{ab}{xy} = 0$.  \carl{Make this clear in the definition itself.}
We focus on quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy for the linear system game $(Hx = c)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{c(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement, and
vice versa.  \carl{This is not entirely true.  A ``quantum strategy presented in terms of projective measurement'' allows
Alice to give answers that violate the ``Constraint satisfaction'' condition, while a ``quantum strategy presented 
in terms of binary observables'' does not.}

It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
operator solution in the following sense.  \carl{There's a missing reference here?}
\begin{definition}[Operator solution of a linear system]
\label{def:op_sol}
	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of bounded Hermitian 
	operators $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
	be best to just state the definition for finite dimensions only.)}
	\begin{enumerate}
		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
		\item for all $1 \leq i \leq m$,
		\begin{align*}
			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
		\end{align*}
	\end{enumerate}
	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
	solution in which the Hilbert space is finite-dimensional.
\end{definition}
Perfect quantum strategies can be extracted from operator solutions and vice versa.
Another angle to look at the linear system game ($Hx = c$) is a finitely presented group
over $\Z_2$, which is called the solution group.
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $Hx = c$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,c) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{c(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
\carl{Don't you also need a commutativity condition for $J$ with $\{ x_i \}$?}
For concepts about group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
Combining \cref{def:op_sol} and \cref{def:presentation}, we know that an operator solution associated to $Hx =c$ is 
a finite-dimensional representation of $\Gamma(H,c)$ that maps $J$ to $-\1$.

\carl{Section 2 needs to be cleaned up in some places, but overall it is pretty good.}

@@

%=======================================
\section{The linear system game}
\label{sec:lsg}
%=======================================
The goal of this section and the following two sections is to 
present a correlation that can self-test $\ket{\EPR{d-1}}$, 
where $d$ is prime and has primitive root $r \in \{2, 3, 5\}$,
and this correlation is denoted by $C(\dr{r})$.  \carl{Be more precise --- we are constructing
such a correlation for any $d$ which has $2, 3,$ or $5$ as a primitive root.}
The correlation we constructed is the optimal correlation for a game $\G(\dr{r})$, which is the combination of two tests.
In this section, we introduce the linear system game which tests a relation that should be satisfied by 
Alice and Bob's observables.

Slofstra's seminal work~\cite{slofstra2017} draws our attention to the relation $xyx^{-1} = y^2$.  \carl{That sentence
is too vague -- either make it a rigorous statement or leave it out.}
The main component of $\G(\dr{r})$ is a linear system game $\LS$, whose solution group is the embedding of the 
following group
\begin{align}
	\Pg_r= \langle u, x : uxu^{-1} = x^r \rangle, \text{ for } r \in \{2, 3,5\}.
\end{align}
In other words, relations in the presentation of the solution group of $\LS_r$ can be combined to derive the
relation $uxu^{-1} = x^r$.  
\begin{proposition}
	\label{prop:embed}
	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
	with constant numbers of variables and equations, where each equation involves $3$ variables.
	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
	that the numbers of variables and equations is independent of $r$, which I'm pretty sure is not true.)}
\end{proposition}
The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Ref.~\cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
and \cref{sec:power5} for $r = 5$.

In the later parts of the paper, we use $n_r$ and $m_r$ to refer to the size of $\LS_r$.
The key feature of this embedding is that $\LS_r$ has constant-sized input-output alphabet
even if the generators $u$ and $x$ have arbitrary order. 
The product of the generators $x_1$ and $x_2$ from the solution group of $\LS_r$ plays the role 
of the generator $x$ in $\Pg_r$ and the product of the generators $x_3$ and $x_4$ plays the role
of the generator $u$ in $\Pg_r$.   \carl{It's reasonable to make a couple informal statements
at the beginning of a section, but you shouldn't be making
such vague statements at this point.  Everything said at this point in the section should have a precise mathematical
meaning.}
As shown in \cref{sec:power2}, \cref{sec:power3} and \cref{sec:power5}, 
$x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
\begin{align}
	(x_3x_4)(x_1x_2)(x_4x_3) = (x_1x_2)^r.
\end{align}
Hence the perfect quantum strategy $(\ket{\psi}, \{A_i, B_i\}_{i=1}^n)$ should satisfy 
the key relation that 
\begin{align}
	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^r\ket{\psi}, 
\end{align}
and similarly on Bob's side.
If we denote the unitary corresponding to the generator $u$ of $\Pg_r$ by $U$ and the unitary
corresponding to $x$ by $X$, then $U = A_3A_4$, $X= A_1A_2$, and 
$UXU\ct \ket{\psi} = X^r \ket{\psi}$.
The special property of $U$ and $X$ is summarized in the following lemma.

\begin{lemma}
	\label{lm:ux_independ}
	Suppose there exist unitaries $U$ and $X$ which have the following forms
	\begin{align}
		X = \sum_{i=1}^{d-1} \omega_d^i \ketbra{i}{i} && U = \sum_{i=1}^{d-1}\ketbra{i/r}{i},
	\end{align}
	where $d$ is an odd prime number with primitive root $r$,
	then the set $\{U^k X^l\}$ for $k=0,1\dots d-2$ and $l = 1,2\dots d-1$ forms a basis of 
	the ring of $(d-1)\times (d-1)$ matrices over $\C$.
\end{lemma}
Note that the unitaries $U$ and $X$ defined in the lemma above satisfy the condition $UXU^\dagger = X^r$.
In the self-test proof, this lemma will be a critical step.
\begin{proof}
We are going to show the $(d-1)^2$ matrices from the set $\{U^k X^l\}_{k \in[d-1], l \in [d-1]+1}$ are linearly independent.
Suppose there exists a set of complex numbers $\{ x_{k,l} \}_{k \in[d-1], l \in [d-1]+1}$
such that 
\begin{align}
	M = \sum_{k=0}^{d-2} \sum_{l=1}^{d-1} x_{k,l} U^k X^l = 0. 
\end{align}
We further assume that there exists a set of integers $\{ k_i \}_{i=1}^{d-1}$ such that $r^{k_i} \equiv i \pmod{d}$.
\carl{We shouldn't be making extra assumptions that are not stated in the lemma.  This looks to me more like
a definition of the variables $\{ k_i \}$, rather than an assumption.}
The fact that $r$ is a primitive root of $d$ guarantees that $k_i$'s are distinct.
Then we can group $\{x_{k,l}\}$ into vectors: $\ket{x_{k_1}}, \ket{x_{k_2}} \dots \ket{x_{k_{d-1}}}$,
where $\ket{x_{k_i}}= (x_{k_i, 1}, x_{k_i, 2} \dots x_{k_i, d-1})^\intercal$.
Our goal is equivalent to proving that $\ket{x_{k_i}} = 0$ for all $i$.
